%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A clean template for an academic CV. This is a short summary version.
%
% Uses tabularx to create two column entries (date and job/edu/citation).
% Defines commands to make adding entries simpler.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper]{article}

% Useful aliases
\newcommand{\SUSTech}{Southern University of Science and Technology}
\newcommand{\Yangtz}{Yangtze University}

% Identifying information
\newcommand{\Title}{CV}
\newcommand{\FirstName}{Daopu}
\newcommand{\LastName}{Wang}
\newcommand{\Initials}{D}
\newcommand{\MyName}{ \FirstName\ \LastName}
% \newcommand{\Me}{\underline{\Initials. \LastName}}  % For citations
\newcommand{\Me}{\underline{\FirstName\  \LastName}}
\newcommand{\Email}{daopuwang77@gmail.com}
\newcommand{\PersonalWebsite}{vianwan.github.io/}
% \newcommand{\LabWebsite}{lethalkiss.github.io/}
% \newcommand{\ORCID}{}

% Names for citing coauthors
\newcommand{\DikunYang}{Dikun Yang}
\newcommand{\Zhentao}{Zhentao Yang}


% Load packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Full Unicode support for non-ASCII characters
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[TU]{fontenc}

% Set main fonts
\usepackage[sfdefault]{atkinson}
\usepackage[ttdefault]{sourcecodepro}

% Icon fonts
\usepackage{fontawesome5}
\usepackage{academicons}

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% For new environments
\usepackage{environ}

% Manage dates and times
\usepackage{datetime}

% Set the page margins
\usepackage{geometry}

% To get the total page numbers (\pageref{LastPage})
\usepackage{lastpage}

% Control spacing in enumerates
\usepackage{enumitem}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Configure section titles
\usepackage{titlesec}

% Fancy header configuration
\usepackage{fancyhdr}

% Control PDF metadata and links
\usepackage[colorlinks=true]{hyperref}

% Custom
\usepackage{xparse}
\usepackage{stackengine}

% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\geometry{%
  margin=12.5mm,
  headsep=0mm,
  headheight=0mm,
  footskip=5mm,
  includehead=true,
  includefoot=true
}

% Custom colors
\definecolor{mediumgray}{gray}{0.5}
\definecolor{lightgray}{gray}{0.9}
\definecolor{mediumblue}{HTML}{2060c2}
\definecolor{lightblue}{HTML}{a0c3ff}
\definecolor{pink}{HTML}{AA5486}
\definecolor{purple}{HTML}{4335A7}
\definecolor{dred}{HTML}{AB4459}
% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.25}

% Remove space between items in itemize and enumerate
\setlist{nosep}

% Set the spacing and format of sections
\titleformat{\section}
  {\normalfont\Large\mdseries} % format
  {} % label
  {0pt} % separation (left separation for hang)
  {} % text before title
  [\titlerule] % text after title
\titlespacing*{\section}
  {0pt} % left pad
  {0.1cm} % before
  {0cm} % after

% Disable number of sections. Use this instead of "section*" so that the sections still
% appear as PDF bookmarks. Otherwise, would have to add the table of contents entries
% manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
% \NewEnviron{EntriesTableDuration}{
% \TablePad
% \begin{tabularx}{\textwidth}{@{}p{0.01\textwidth}@{\hspace{0.02\textwidth}}p{0.97\textwidth}@{}}
%   \BODY
% \end{tabularx}
% \TablePad
% }
% Define EntriesTableDuration new enviroment
\newcommand{\TablePad}{\vspace{-0.2cm}}
\NewEnviron{EntriesTableDuration}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.08\textwidth}@{\hspace{0.02\textwidth}}p{0.90\textwidth}@{}}
  \BODY
\end{tabularx}
\TablePad
}
\NewEnviron{EntriesTableYear}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.05\textwidth}@{\hspace{0.01\textwidth}}p{0.94\textwidth}@{}}
  \BODY
\end{tabularx}
\TablePad
}
\NewEnviron{EntriesNote}{
  \TablePad
  \begin{tabularx}{\textwidth}{@{}p{0.14\textwidth}@{\hspace{0.01\textwidth}}p{0.85\textwidth}@{}}
    \BODY
  \end{tabularx}
  \TablePad
}
\NewEnviron{EntriesDate}{
  \TablePad
  \begin{tabularx}{\textwidth}{@{}p{0.08\textwidth}@{\hspace{0.01\textwidth}}p{0.91\textwidth}@{}}
    \BODY
  \end{tabularx}
  \TablePad
}
\NewEnviron{EntriesTableDurationBack}{
  \TablePad
  \begin{tabularx}{\textwidth}{@{}p{0.0\textwidth}@{\hspace{0.01\textwidth}}p{0.99\textwidth}@{}}
    \BODY
  \end{tabularx}
  \TablePad
}
% Macros to set the year and duration on the left column
% \newcommand{\Duration}[2]{\fontsize{10pt}{0}\selectfont \texttt{#1-#2}}
\newcommand{\Duration}[2]{%
  \fontsize{10pt}{12pt}\selectfont
  \Shortunderstack[c]{\texttt{#1} $\downarrow$ \texttt{#2}}
}
\newcommand{\Year}[1]{\fontsize{10pt}{0}\selectfont \texttt{#1}}
\newcommand{\Colon}[1]{\fontsize{10pt}{0}\selectfont \texttt{#1:}}
\newcommand{\OColon}[1]{\fontsize{10pt}{0}\selectfont \texttt{#1}}
\newcommand{\Month}[2]{\fontsize{10pt}{0}\selectfont \texttt{#1 #2}}
\newcommand{\Ongoing}{on}
\newcommand{\Future}{future}
\newcommand{\replacehyphenwithcolon}[1]{\StrSubstitute{#1}{-}{:}}
\newcommand{\FixedRightSpace}[1]{\hfill\makebox[7em][l]{#1}}

% Macros to add links and mark publications
\newcommand{\DOI}[1]{doi:\href{https://doi.org/#1}{#1}}
\newcommand{\Website}[1]{\href{https://#1}{#1}}
\newcommand{\Preprint}[1]{Preprint: \href{https://doi.org/#1}{#1}}
\newcommand{\GitHub}[1]{\faGithub{} \href{https://github.com/#1}{#1}}
\newcommand{\Data}[1]{\faChartBar{} doi:\href{https://doi.org/#1}{#1}}

% Define command to insert month name and year as date
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Configure a fancy footer
\newcommand{\Separator}{\hspace{3pt}|\hspace{3pt}}
\newcommand{\FooterFont}{\footnotesize\color{mediumgray}}
\pagestyle{fancy}
\fancyhf{}
\lfoot{%
  \FooterFont{}
  \MyName{}
  \Separator{}
  \Title{}
}
\rfoot{%
  \FooterFont{}
  Last updated: \monthyear\today{}
  \Separator{}
  \thepage\space of\space \pageref*{LastPage}
}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{1pt}
\preto{\footrule}{\color{lightgray}}

% Metadata for the PDF output and control of hyperlinks
\hypersetup{
  colorlinks,
  allcolors=mediumblue,
  breaklinks=true,
  pdftitle={\Title{} - \MyName},
  pdfauthor={\MyName},
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{minipage}[t]{0.5\textwidth}
  {\fontsize{20pt}{0}\selectfont\textcolor{purple}{\MyName}}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \begin{flushright}
    \Title{}
  \end{flushright}
\end{minipage}
\\[-0.1cm]
\textcolor{lightgray}{\rule{\textwidth}{3pt}}
\begin{minipage}[t]{0.5\textwidth}
  Tel: +8617340544463
  \\
  Email: \href{mailto:\Email}{\Email}
  \\
  Homepage: \Website{\PersonalWebsite}
  % \\
  % Research Group: \Website{\LabWebsite}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \begin{flushright}
  \SUSTech
  \\
  Department of Earth and Space Sciences
  \\
  Master Candidate in Physics
  \end{flushright}
\end{minipage}
\vspace{0.3cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\textcolor{purple}{Educations}}

\begin{EntriesTableDurationBack}
  % \Duration{2022.09}{2025.06}  &
  &
  \textcolor{pink}{\textbf{MS in Physics}}, \SUSTech, Shenzhen, China.\FixedRightSpace{2022.09 - 2025.06}
  \newline
  GPA: 3.56/4.0
  \newline
  Courses: Advanced Geo-Electromagnetism, Computational Geophysics, Geophysical Inverse Problem
  \newline
  Thesis: Electric Resistivity Tomography Guided by Seismic Information and Its Application in Karst Cavities
  \newline
  Advisor: \DikunYang.
  \\
  % \Duration{2018.09}{2022.06}  &
  &
  \textcolor{pink}{\textbf{BS in Geophysics}}, \Yangtz, Wuhan, China.\FixedRightSpace{2018.09 - 2022.06}
  \newline
  GPA: 3.73/5.0, Rank: 4/43
  \newline
  Courses: Principles of Seismic Exploration, General Geological Practice
  \newline
  Thesis: Characteristics of MT Signals Based on Remote Reference Station Statistical Analysis Research
  \newline
  Advisor: Xinbing Xie.
\end{EntriesTableDurationBack}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\textcolor{purple}{Publication}}

\begin{EntriesTableYear}
  \Year{2024} &
  \textbf{Underwater ERT method to image Karst cave distribution below the river water}.
  \newline
  \Me, \DikunYang, et al.,
  (2024), SEG Global Meeting Abstracts: 139-142. %AI Ain, UAE, 16-19 October 2023.
  DOI: \href{https://library.seg.org/doi/10.1190/iceg2023-032.1}{10.1190/iceg2023-0321.1}
  \\
\end{EntriesTableYear}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\textcolor{purple}{Research Experience}}

\begin{EntriesTableDurationBack}
  &
  \textbf{Comprehensive Geophysical Prospecting of Geo-Hazards in the SUSTech Campus}.\FixedRightSpace{2024.10 - Present}
  \begin{itemize}[label={-}, leftmargin=*] % 使用 - 作为项目符号，leftmargin=* 使缩进与文本对齐
    % \item \textbf{Southern Marine Science and Engineering Guangdong laboratory(Zhuhai) supports this research}.
    \item \textit{Leading teams through the entire process of Electric Resistivity Tomography (ERT) survey design, data acquisition, data processing, and data interpretation}.
    \item \textit{Using the open Python package SimPEG process potential difference data to obtain conductivity cross-section}.
    \item \textit{Participating in acquisition and processing seismic data from both active and passive sources using Smart Seismic Sensor IGU-16HR}.
    \item \textit{Extracted dispersion curves from active sources using the Multi-channel Analysis of Surface Waves (MASW) method, including FK and LRT techniques, and from ambient noise using SPAC and F-K methods, then inverted these dispersion curves to obtain Vs structures}.
    % \item \textit{Extract dispersion curves from ambient noise using SPAC and F-J methods and get Vs structures}.
  \end{itemize}
  \\
  &
  \textbf{Development of a Cloud-Based Simulation Platform for Direct Current Resistivity Imaging}.\FixedRightSpace{2024.10 - Present}
  \begin{itemize}[label={-}, leftmargin=*]
    \item \textit{Simulation of electric potential distribution using the finite volume method}.
    \item \textit{Designed a user-friendly interface with customizable parameters for professional use}.
    \item \textit{Cloud-based deployment and out-of-the-box functions, secure and stable.}
    \item \textit{In a short period of time, get the high-resolution underground electrical structure as well as iteration parameters, model parameters and so on}.
  \end{itemize}
  \\
  &
  \textbf{Experiment of Nearshore Magnetotelluric (MT) Survey Using Inter-station Impedance}.\FixedRightSpace{2024.10 - 2024.11}%Experiment of Nearshore Magnetotelluric (MT) Survey using Inter-station Impedance Method.} 
  % \textit{}
  \begin{itemize}[label={-}, leftmargin=*] % 使用 - 作为项目符号，leftmargin=* 使缩进与文本对齐
    % \item \textbf{Southern Marine Science and Engineering Guangdong laboratory(Zhuhai) supports this research}.
    \item \textit{Design schemes for shallow water MT surveys including underwater cable design, site evaluation}.
    \item \textit{Acquisite MT field data both onshore and offshore using Phoenix instrument MTU-5A.}
    \item \textit{Processing obtained inter-station time series and estimation of impedance by SSMT2000 and MTEditor.}
  \end{itemize}
  \\
  &
  \textbf{Underwater ERT Method to Image Karst Cave Distribution Below River Water}.\FixedRightSpace{2023.02 - 2023.10}
  \newline
  Project from CCCC-FHDI Engineering Co., Ltd.
  \begin{itemize}[label={-}, leftmargin=*] % 使用 - 作为项目符号，leftmargin=* 使缩进与文本对齐
    % \item \textbf{CCCC-FHDI Engineering Co., Ltd, supports this research}.
    \item \textit{As Karst caves were covered by river water with rapid flow, a specialized underwater cable and well-designed ERT measurements were adopted to obtain river bottom potential difference data}.
    \item \textit{2D inversion models incorporating riverbed terrain were obtained, successfully corresponding with existing borehole data.}
    % \item \textit{An oral report was presented at the 7th ICEG conference and a conference paper was published}.
  \end{itemize}
  \\
  &
  \textbf{Imaging Karst Cavities Distribution Using ERT and ANT Method}.\FixedRightSpace{2022.11 - 2023.02}
  \newline
  Project from Shenzhen Municipal Engineering Corp.
  \begin{itemize}[label={-}, leftmargin=*] 
    % \item \textit{Acquisition of ERT data and Seismic data in site and data processing}.
    \item \textit{Acquired and processed ERT and seismic data on-site, successfully identifying the spatial position of the cave using conductivity and velocity models}.
    \item \textit{By incorporating velocity structures as a new soft constraint, the resolution of the conductivity model was successfully improved}.
  \end{itemize}
  \\
  &
  \textbf{Cross-hole Electrical Resistivity Tomography (CHERT) for Monitoring DNAPL Contamination.}\FixedRightSpace{2022.07 - 2022.11}
  \begin{itemize}[label={-}, leftmargin=*] 
    \item \textit{Utilized a monitoring well as an electrode to transmit current}.
    \item \textit{Acquired ERT data from both surface and well-based electrodes for comprehensive subsurface analysis}.
    \item \textit{Mapped the direction and depth of pollutant dispersion by analyzing resistivity anomalies}.
    % \item \textit{An oral report was presented at the IMAGE2023 conference}.
  \end{itemize}
\end{EntriesTableDurationBack}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\textcolor{purple}{Awards and Fellowships}}

\begin{EntriesDate}
  \OColon{2023.10} &
  The \textbf{\textcolor{pink}{Third Prize}} in the eighth National College Students  "Innovation Cup" Geophysical Knowledge Competition (CNY 1000).
  \href{https://newshub.sustech.edu.cn/html/202306/43985.html}{\textcolor{blue}{News Report}}
  \\
  \OColon{2021.09} &
  The \textbf{\textcolor{pink}{Second Prize}} in the seventh National College Students "Innovation Cup" Geophysical Knowledge Competition.
  \\
  \OColon{2019.12} &
  \textbf{\textcolor{pink}{The National Encouragement Scholarship}} (CNY 5000).
  \\
\end{EntriesDate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\textcolor{purple}{Presentations}}

\begin{EntriesDate}
  \Year{2024.08} &
  \textbf{Interpreting Cross-river Underwater Electric Resistivity Data for Dam Construction: Lessons Learned from 2D and 3D Inversions}.
  \newline
  \Me, \DikunYang,
  \textit{The International Meeting for Applied Geoscience and Energy
  \href{https://www.imageevent.org/}{ (IMAGE2024) }}, Aug. 28, 2024, Houston, Texas, USA.
  \\
  \Year{2024.06} &
  \textbf{Development and Application of Joint Nodal Acquisition Stations for Seismic and ERT Data}.
  \newline
  \Me, \DikunYang,
  \textit{The 11th International Conference on Environmental and Engineering Geophysics
  \href{https://ess.sustech.edu.cn/iceeg2024/}{ (11th ICEEG) }}, Jun. 30, 2024, Shenzhen, China.
  \\
  \Year{2023.10}  &
  \textbf{Underwater ERT Method to Image Karst Cave Distribution Below the River Water}.
  \newline
  \Me, Haibing Chai, \DikunYang,
  \textit{The Seventh International Conference on Engineering Geophysics
  \href{https://conferences.uaeu.ac.ae/iceg2023/en/}{ (7th ICEG) }}, Oct. 18, 2023, AI Ain, UAE.
  \\
  \Year{2023.08} &
  \textbf{Electric Resistivity Tomography Inversion Guided by Passive Microtremor Data for Detection of Karst Cavities}.
  \newline
  \Me, \DikunYang, \Zhentao,
  \textit{The International Meeting for Applied Geoscience and Energy
  \href{https://www.imageevent.org/}{ (IMAGE2023) }}, AUG. 27, 2023, Houston, Texas, USA.
\end{EntriesDate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\textcolor{purple}{Languages \& Skills}}

\begin{EntriesNote}
  \Colon{\textbf{Programming}} &
  Python, MATLAB, Jekyll, Linux, etc.
  \\
  \Colon{\textbf{Software}} & 
  SimPEG, SSMT2000, SAC, Adobe (Photoshop, Lightroom), Cartopy, Disba, etc.
  \\
  \Colon{\textbf{Instruments}} &
  SmartSolo Geophone, Phoenix System MTU-5A, Multi-channel Electrical System GD-20, RTK, etc.
  \\
  \Colon{\textbf{Languages}} &
  Mandarin (Native), English (IELTS 6.5).
  \\
  \Colon{\textbf{Geophysical Skills}} &
  ERT (Practical experience of the whole-process ERT survey);
  MT (Experience in data acquisition and data processing);
  Surface Wave (Field practice and seismic data processing).
\end{EntriesNote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\textcolor{purple}{Interests}}

\begin{EntriesNote}
  \Colon{\textbf{Sports}} &
  Swimming, hiking.
  \\
  \Colon{\textbf{Photography}} &
  \href{https://www.xiaohongshu.com/user/profile/5f8ef7ff0000000001002b56}{Photography Portfolio} featuring landscapes and emotional moments.
  \\
  \Colon{\textbf{Volunteering}} &
  Conference volunteering (more than 100 hours); maintain individual dedication and zest for life firsthand.
\end{EntriesNote}

\end{document}
